%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{calc} % added
\usepackage{ragged2e}

\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    \begin{minipage}[t]{0.99\linewidth} % Adjust the width as needed
      {#1}
    \end{minipage}
    \vspace{1pt} % Adjust the space between elements as needed
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheadingLeftOneRow}[2]{% % added
\begin{description}[leftmargin=!,labelwidth=\widthof{\small\bfseries #1}]
    \item[\small #1]{\textit{\small  #2}}
\end{description}
}

\newcommand{\resumeSubSubheadingLeftTwoRows}[4]{%
\begin{description}[leftmargin=!,labelwidth=\widthof{\small\bfseries #1}]
    \item[\small #1]{\textit{\small  #2}}
    \item[\small #3]{\textit{\small  #4}}
\end{description}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Pavel Zolotarev} \\ \vspace{1pt}
    \small +31-6-2941-3124
    $|$ {\small{pavel@pavelzol.me}}
    $|$ \href{https://linkedin.com/in/pavelzol}{\underline{linkedin.com/in/pavelzol}}
\end{center}


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Java Software Engineer}{Aug. 2023 -- Present}
      {Picnic Technologies}{Amsterdam, Netherlands}
      \resumeItemListStart
        \resumeItem{Led integration of traditional search with LLM engine, resulting in up to 16\% increase of conversion rate.}
        \resumeItem{Refactored the logic for recipe search and indexing to ensure that recipes are loaded from a single source of truth within the company.}
      \resumeItemListEnd

    \resumeSubheading
      {Engineering Manager}{Dec. 2022 -- Aug. 2023}
      {Exness}{Limassol, Cyprus}
      \resumeItemListStart
        \resumeItem{Led development and support of a corporate platform for omnichannel customer communications with strict requirements for latency and availability.}
        \resumeItem{Initiated migration of the communication service to event sourcing pattern, resulting in reduction of request latency from 400ms to 100ms on 95th percentile.}
        \resumeItem{Recruited and integrated highly skilled and experienced professionals, resulting in a stronger team.}
    \resumeItemListEnd

    \resumeSubheading
      {Java Software Engineer}{Dec. 2021 -- Sep. 2022}
      {Revolut}{Moscow, Russia}
      \resumeItemListStart
        \resumeItem{Led analysing, development and acceptance testing of Debit Card Overdraft product, a feature allowing customers to overdraw their debit card accounts up to a specified limit, preventing transaction declines. Ensured full compliance with legal requirements for the UK and EU markets.}
        \resumeItem{Designed the solution architecture for a set of features ensuring the bank's compliance with Regulation Z requirements set by the US Federal Reserve Board.}
    \resumeItemListEnd

    \resumeSubheading
      {Engineering Manager}{Feb. 2019 -- Jun. 2021}
      {Raiffeisen Bank}{Moscow, Russia}
      \resumeItemListStart
        \resumeItem{Led and managed team working on several Cash Management products. Built up from the scratch processes of analysing, development, testing and releasing features.}
        \resumeItem{Developed brand new system for handling corporate deposits. The system was built using microservice architecture, with close to real time Money Market quoting integration.}
    \resumeItemListEnd

    \resumeSubheading
      {Big Data / Java Developer}{Apr. 2016 -- Feb. 2019}
      {DataArt}{Voronezh, Russia}
      \resumeItemListStart
        \resumeItem{As a fullstack participated in development of e-commerce system, transitioned it to SPA front-end architecture.}
        \resumeItem{Developed Hadoop based datalake and ETL pipeline on Spark for one of the biggest pharmaceutical companies of USA.}
    \resumeItemListEnd

    \resumeSubheading
      {Big Data Developer}{Aug. 2013 -- Mar. 2016}
      {AT Consulting}{Voronezh, Russia}
      \resumeItemListStart
        \resumeItem{Developed Hadoop based datalake using Spark and MapReduce for industry leading telecom operator.}
    \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Voronezh State Technical University}{2013 -- 2017}
      {Bachelor of Science in Information Technology}{Voronezh, Russia}
  \resumeSubHeadingListEnd

%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, JavaScript, Python, SQL } \\
     \textbf{Frameworks}{: Spring Boot, Reactor, Apache Spark, Hadoop, AngularJS, CamundaBPMN } \\
     \textbf{Data Storage Systems}{: PostgreSQL, MongoDB, Redis, OpenSearch, HDFS, Hbase, Kafka } \\
     \textbf{Developer Tools}{: Maven, Gradle, Git, Liquibase, DataDog, Grafana } \\
     \textbf{CI/CD and Cloud}{: OpenAI, GitLab CI/CD, Docker, Kubernetes, AWS } \\
     \textbf{Communication}{: Agile, Hiring, Performance Review, Crossteam Communication, Stakeholder Management } \\
    }}
 \end{itemize}


%-----------LANGUAGES-----------
\section{Languages}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{English}{: Proficient (C1)} \\
     \textbf{Russian}{: Native}
    }}
 \end{itemize}
%-------------------------------------------
\end{document}
